---
title: "TidyTuesday 2021 Week 6: HBCU Enrolment"
description: |
  A short description of the post.
author:
  - name: Kyle Belanger
    url: {}
date: 02-03-2021
categories:
  - TidyTuesday
output:
  distill::distill_article:
    self_contained: false
    toc: TRUE
    code_folding: TRUE
draft: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

# Introduction



# Load Data

```{r}
library(dplyr)

bach_students_raw <- readxl::read_xlsx("104.10.xlsx", sheet = 2)

glimpse(bach_students_raw)

```


We can see we have some wild column names, as well as a column named total, which is actually just the year column.  Due to some characters in each column, ever column has been read in as a character, when in reality they should be numeric, lets fix this first.  I also don't like that prior to 1985, years are sporadic, so lets just focus on 1985 and on.  I will finish here with renaming the Total column to year.

```{r}

bach_students <- bach_students_raw %>% 
  mutate(across(everything(), as.numeric)) %>% 
  filter(Total >= 1985) %>% 
  rename(year = Total)

```

Pivot_longer 
#TODO: Explain why

```{r}

bach_students_long <- bach_students %>% 
  tidyr::pivot_longer(-year)

```







